\textls[-0]{\thetitle}

### 2023-03-18 metatheory-condensed.tex
more details

For each pair of types identifying a constructor, the first type may be thought of
as the non-inductive part of the constructor, and the second type as the arity
of the inductive part.
For example, the signature~$\wsig_{\texttt{tm}}$ of the W-type modeling
the inductive type~\lsti{tm} (\cref{fig:stlc-mechanized})
is constructed as follows,
where $\bbzero$ is the bottom type~$\bot$, $\bbone$ the unit type~$\top$, $\bbtwo$ the boolean type,
and $T_{\texttt{id}}$ a type encoding~\lsti{id}:
%
\begin{align*}
\small
\begin{tabular}{@{}llll@{}}
\lsti!tm_unit : tm!
&
\lsti!tm_var : id -> tm!
&
\lsti!tm_abs : id -> tm -> tm!
&
\lsti!tm_app : tm -> tm -> tm!
\smallskip\\
$\wsig_{\texttt{tm}}^0 \coloneq \WSigAdd{\WSigEmp}{\bbone}{\lambda \_ . \bbzero}$ 
& $\wsig_{\texttt{tm}}^1 \coloneq \WSigAdd{\wsig_{\texttt{tm}}^0}{T_{\texttt{id}}}{\lambda \_ . \bbzero}$
& $\wsig_{\texttt{tm}}^2 \coloneq \WSigAdd{\wsig_{\texttt{tm}}^1}{T_{\texttt{id}}}{\lambda \_ .\bbone} $ 
& $\wsig_{\texttt{tm}} \coloneq \WSigAdd{\wsig_{\texttt{tm}}^2}{\bbone}{\lambda \_ .\bbtwo}$
\end{tabular}
\end{align*}

\noindent
Thus, the encoding of \lsti{tm_abs} has type
$T_{\texttt{id}} \to (\bbone \to \El{\wcode{\wsig_{\texttt{tm}}}}) \to \El{\wcode{\wsig_{\texttt{tm}}}}$,
and that of \lsti{tm_app} has type
$\bbone \to (\bbtwo \to \El{\wcode{\wsig_{\texttt{tm}}}}) \to \El{\wcode{\wsig_{\texttt{tm}}}}$.
These types are strictly positive by construction.

>>>>

For each pair of types identifying a constructor, the first type models
the non-inductive arguments of the constructor, and the second type models the \emph{arity}
of the inductive arguments.
For example, the signature~$\wsig_{\texttt{tm}}$ of the W-type modeling
the inductive type~\lsti{tm} (\cref{fig:stlc-mechanized})
is constructed as follows,
where $\bbzero$ is the bottom type~$\bot$, $\bbone$ the unit type~$\top$, $\bbtwo$ the boolean type,
and $T_{\texttt{id}}$ a type encoding~\lsti{id}:
%
\begin{align*}
\small
\begin{tabular}{@{}llll@{}}
\lsti!tm_unit : tm!
&
\lsti!tm_var : id -> tm!
&
\lsti!tm_abs : id -> tm -> tm!
&
\lsti!tm_app : tm -> tm -> tm!
\smallskip\\
$\wsig_{\texttt{tm}}^0 \coloneq \WSigAdd{\WSigEmp}{\bbone}{\lambda \_ . \bbzero}$ 
& $\wsig_{\texttt{tm}}^1 \coloneq \WSigAdd{\wsig_{\texttt{tm}}^0}{T_{\texttt{id}}}{\lambda \_ . \bbzero}$
& $\wsig_{\texttt{tm}}^2 \coloneq \WSigAdd{\wsig_{\texttt{tm}}^1}{T_{\texttt{id}}}{\lambda \_ .\bbone} $ 
& $\wsig_{\texttt{tm}} \coloneq \WSigAdd{\wsig_{\texttt{tm}}^2}{\bbone}{\lambda \_ .\bbtwo}$
\end{tabular}
\end{align*}

\noindent
While \lsti{tm_unit} and \lsti{tm_var} have no inductive arguments,
\lsti{tm_abs} has one and \lsti{tm_app} has two.
The encoding of \lsti{tm_abs} has type
$T_{\texttt{id}} \to (\bbone \to \El{\wcode{\wsig_{\texttt{tm}}}}) \to \El{\wcode{\wsig_{\texttt{tm}}}}$,
and that of \lsti{tm_app} has type
$\bbone \to (\bbtwo \to \El{\wcode{\wsig_{\texttt{tm}}}}) \to \El{\wcode{\wsig_{\texttt{tm}}}}$.
These types are strictly positive by construction.
